%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventrynew
  	{\href{http://www.qbm.genzentrum.lmu.de/}{QBM - Graduate School}, Ludwig-Maximilians University, Max-Planck Institute for Biophysical Chemistry}
  	{PhD in Computational Biology (1.0 'magna cum laude')} 
	{Munich and Goettingen, Germany}
	{Oct. 2013 - Dec. 2017}
	{
		\begin{cvitems}
			\item {Thesis in the \href{http://www.mpibpc.mpg.de/soeding}{Soeding lab}: \href{https://edoc.ub.uni-muenchen.de/21635/}{Bayesian Statistical Approach for Protein Residue-Residue Contact Prediction} }
			\item {Applying Bayesian statistical modeling and machine learning approaches for prediction of physical contacts between amino acid side chains in the protein structure given only sequence data of the protein family}
			\item {Working in a Linux environment with Python and R, focusing on efficient parallelizable code via C++ extensions, favouring reproducible solutions via packaging/automation and good documentation style}
			\item{Working through a full data science workflow: data preparation, explorative analysis, building predictors and models, validating assumptions, simulating synthetic data, benchmarking and visualizing data}
		\end{cvitems}
	}
	{4 yrs 3 mos}

%---------------------------------------------------------
  \cventrynew
  	{Ludwig-Maximilians University and Technical University}
    {Master of Science in Bioinformatics (1.1, among 10\% best)} 
	{Munich, Germany}
	{Oct. 2011 - Sep. 2013}
	{
		\begin{cvitems}
			\item {Master thesis in the \href{http://www.mpibpc.mpg.de/soeding}{Soeding lab} (1.0):\\
			Improving constraints from statistical coupling analysis for de-novo protein structure prediction using amino acid pair propensities}
			\item {Main focus on explorative data analysis and visualisation of preprocessed data to obtain meaningful insights into the research problem and building simple statistical models and predictors using R}
		\end{cvitems}
	}
	{2 yrs}

%---------------------------------------------------------
  \cventrynew
    {Johann-Wolfgang-Goethe University } % Institution
    {Bachelor of Science in Bioinformatics (1.1, among 10\% best)} % Degree
    {Frankfurt am Main, Germany} % Location
    {Oct. 2008 - Sep. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Bachelor thesis with \href{mailto:ina.koch@bioinformatik.uni-frankfurt.de}{Prof. Dr Ina Koch} and Dr. Christian Buning  @Sanofi-Aventis Deutschland GmbH (1.0):\\Homologiemodellierung, Struktur-Wirkungsbeziehungen und Selektivitätsanalyse von SGLT Transportern}
      \end{cvitems}
    }
    {3 yrs}


%---------------------------------------------------------
  \cventrynew
    {Max-Klinger Gymnasium and Lamar County High School} % Institution
    {Abitur (1.0) } % Degree
    {Leipzig, Germany} % Location
    {Sept. 1997 - Jun. 2006} % Date(s)
    {
    \begin{cvitems}
	    \item {Taking advanced courses English and Math}
    	\item {Obtaining a High School Diploma as an exchange student in Vernon, AL, USA (Sep 2003 - May 2004)}
    \end{cvitems}
    }
    {13 yrs}

    
%---------------------------------------------------------
\end{cventries}
